Sparse spectral methods for partial differential equations on spherical caps

### 2020-12-21 papers/spherical-caps/spherical-caps.tex
add grant support
Added EPSRC acknowledgement. Minor edits to paper.

@@

\begin{figure}[t]
	\centering % <-- added
	\includegraphics[scale=0.35]{complexity-Nend=1000}
	\caption{Time in seconds to  to build and solve the system $\big[\DeltaS + v(x,y,z) \big] \: u(x,y,z) = f(x,y,z)$. This demonstrates that the approach is roughly of order $\bigO(N^2)$, where $N$ is the degree to which we approximate the solution. Here, we used $f = -2e^{x}yz(2+x) + (z - \alpha) e^{x} (y^3 + z^2 y - 4xy - 2y)$.}
	\centering
	\label{fig:complexity}
\end{figure}

@@

In Figure~\ref{fig:complexity} we plot the time taken\footnote{measured using the \enquote{@belapsed} macro from the BenchmarkTools.jl package \cite{BenchmarkTools.jl-2016} in Julia.}  to construct the operator for $\DeltaS + v(x,y,z)$, this time with a rotationally invariant $v(x,y,z) = \cos z$, and solve a zero boundary condition Helmholtz problem. The plot demonstrates that as we increase the degree of approximation $N$, we achieve a complexity of an optimal $\bigO(N^2)$.

>>>>

\noindent{\bf Acknowledgments}: The first author was supported by the Engineering and Physical Sciences Research Council Mathematics of Planet Earth Centre for Doctoral Training at Imperial College London and the University of Reading, with grant number EP/L016613/1.The second author was supported by the Leverhulme Trust Research Project Grant RPG-2019-144 ``Constructive approximation theory on and inside algebraic curves and surfaces''.

@@

\begin{figure}[t]
	\centering % <-- added
	\includegraphics[scale=0.35]{complexity-Nend=1000}
	\caption{Time in seconds to build and solve the system $\big[\DeltaS + v(x,y,z) \big] \: u(x,y,z) = f(x,y,z)$, for a rotationally invariant $v(x,y,z) = v(z)$. This demonstrates that the approach is roughly of order $\bigO(N^2)$, where $N$ is the degree to which we approximate the solution. Here, we used $f = -2e^{x}yz(2+x) + (z - \alpha) e^{x} (y^3 + z^2 y - 4xy - 2y)$ and $v(x,y,z) = v(z) = \cos(z)$.}
	\centering
	\label{fig:complexity}
\end{figure}

@@

In Figure~\ref{fig:complexity} we plot the time taken\footnote{measured using the \enquote{@belapsed} macro from the BenchmarkTools.jl package \cite{BenchmarkTools.jl-2016} in Julia.} to construct the operator for $\DeltaS + v(x,y,z)$, with a rotationally invariant $v(x,y,z) = v(z) = \cos z$, and solve a zero boundary condition Helmholtz problem. The plot demonstrates that as we increase the degree of approximation $N$, we achieve a complexity of an optimal $\bigO(N^2)$.
